COG-ED Manuscript

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
added plot to supplementary
started setting up the SCA

However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
RTs were longer for 3- than 2-back (`r apa_print(pairs(emmeans(object = hypothesis1b_rmanova$aov,specs = "level"))[1]`), but not different between 2- and 4-back or 3- and 4-back.
Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.

@@

@@

`r h2b_ss.table`

>>>>

However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
RTs were longer for 3- than 2-back (`r apa_print(pairs(emmeans(object = hypothesis1b_rmanova$aov,specs = "level")))[1]`), but not different between 2- and 4-back or 3- and 4-back.
Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.

@@

```{r SpecificationCurveAnalysis, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

  # Here we repeat the multi level model with all analysis pipelines.

    sca_data <- pipelines_data[[i]]

    # get a subset without RT = NA

    sca_data <- droplevels(subset(sca_data[ ,c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")], subset = !is.na(rt)))

    # center the predictors

        # centering the level 1 predictors (d', RT, level, correct, postcorrect) within cluster

        sca_data$dprime.cwc       <- sca_data$dprime - (ave(sca_data$dprime, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
        sca_data$rt.cwc           <- sca_data$rt - (ave(sca_data$rt, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
        sca_data$level.cwc        <- sca_data$level - (ave(sca_data$level, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
        sca_data$correct.cwc      <- sca_data$correct - (ave(sca_data$correct, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
        sca_data$postcorrect.cwc  <- sca_data$postcorrect - (ave(sca_data$postcorrect, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))

        # centering the level 2 predictor NFC at the grand mean

        sca_data$nfc.cgm <- scale(sca_data$nfc, scale = F)

    # define the null model

    m0_sca <- lmer(sv ~ 1 + (1|subject), data = sca_data, REML = T)

    # intra-class-correlation

    var_m0_sca <- as.data.frame(VarCorr(m0_sca))
    icc_sca <- var_m0_sca$vcov[1] / (var_m0_sca$vcov[1] + var_m0_sca$vcov[2])

@@

`r h2b_ss.table`
`r h2b_ss.plot`
